---
title: "Week 7 Assignment - Solutions"
author: "Jose Luis Rodriguez Gil"
date: "28/10/2020"
output: 
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load packages, include=FALSE}

library(tidyverse)
library(janitor)
library(here)
library(viridis)
library(lubridate)
library(patchwork)

```

I have previously created my theme as a function in a separate r script file (`.R`) which has been saved in the `fucntions` folder. We need to source this function so it is available for us to use.

Feel free to go check the `.R` file to see how i created my Theme. I actually started from scratch instead of modifying an existing one, so i specified the values i wanted for all possible parameters.

```{r source theme function}

source(here("functions", "theme_pepe.R"))

```

We load the two data sets we are going to use for this execise. One containing the chlorophyll a data and the other with the phosphorus measurements. All data collected at **FortWhite Alive** and available [here](http://lwbin-datahub.ad.umanitoba.ca/dataset/fortwhyte-alive-model-watershed-project)

```{r load data}

chll_a <- read_csv(here("data", "chlorophyll_a.csv"))
phosphorus <- read_csv(here("data", "phosphorus_profiles.csv"))

```

# Plots

## Chlorophyll a plot

First we start with the chlorophyll a plot. As mentioned in the instructions, we want to create a summary plot of cholorophyll concentrations in the surface of the different lakes using the theme we have created. In this case, i am using a violin plot with a `geom_gitter()` to show the actual data.

```{r chll_a_plot}

chll_a_plot <- chll_a %>% 
  clean_names() %>% 
  filter(sample_depth_m == 0) %>% 
  ggplot() +
  
  #Main plotting elements
  geom_violin(aes(x = lake_name, y = chlorophyll_concentration_ug_l), color = "white", fill = NA) +
  geom_jitter(aes(x = lake_name, y = chlorophyll_concentration_ug_l), color = "white", alpha = 0.5, width = 0.1, height = 0) +
  
  #scales
  # scale_y_log10() +
  # annotation_logticks(sides = "l", color = "white") +
  
  #theme and formatting
  theme_pepe() +
  labs(x = NULL,
       y = expression(Chlorophyll~a~concentration~(mu*g~.~L^{-1})))

print(chll_a_plot)

``` 

## Phosphorus plot

Now we create the phosphorus. As mentioned in the instructions, we want to create a summary plot of total phosphorus concentrations in the surface of the different lakes using the theme we have created. In this case, i am using a violin plot with a `geom_gitter()` to show the actual data.

```{r p_plot}

p_plot <- phosphorus %>% 
  clean_names() %>% 
  filter(sample_depth_m == 0) %>% 
  ggplot() +
  
  #Main plotting elements
  geom_violin(aes(x = lake_name, y = total_phosphorus_mg_l), color = "white", fill = NA) +
  geom_jitter(aes(x = lake_name, y = total_phosphorus_mg_l), color = "white", alpha = 0.5, width = 0.1, height = 0) +
  
  # Scales
  # scale_y_log10() +
  # annotation_logticks(sides = "l", color = "white") +

  #Theme and formating
  theme_pepe() +
    labs(x = NULL,
       y = expression(Total~phosphorus~(m*g~.~L^{-1})))

print(p_plot)

```

## Combined plot

Finally, we are going to use the`{patchwork}` package to create a combined plot.

```{r combined_plot}

combined_plot <- chll_a_plot + p_plot +
  plot_layout(ncol = 1) +                  # We specify that we want them one on top of the other
    plot_annotation(tag_levels = "A") &    # We add the panel annotation so they can be referenced in the figure caption
  theme_pepe()                             # Using the `&` we can apply the theme also to the combined plot, 
                                           # this is needed to ensure my dark background is mainatined in the combined plot background

print(combined_plot)

ggsave(here("figures", "combined_plot.pdf"), combined_plot,
       width = 190, height = 140, units = "mm") 

ggsave(here("figures", "combined_plot.png"), combined_plot,
       width = 10, height = 7, units = "in") # i am saving a .png copy so i could embed it in the README.md

```

